### 2020-11-16 latex/sections/background.tex
latexing

The algorithms that are used in traditional state-space searches are for instance Depth-first search (DFS), Breadth-first Search (BFS), Alpha-Beta Pruning Search (AB-Search), and Monte-Carlo Tree Search (MCTS).

@@

In the algorithm Monte-Carlo Tree Search, there is an agent within some environment. Where each node in the environment represents a state-action pair of the environment, by state-action pair what is meant it is some state and the action that brought the agent to that state. This pair should be unique within the environment.

@@

Many algorithms are popular in reinforcement learning, for instance Q-learning(CITE ME), CARLA (CITE ME),
and many others.

@@

Neural networks are machine learning models that take in as input anything numerical and they apply continuous differentiable functions to that input s.t. they end with some output. This output is then compared to the expected output the difference between these outputs is called a loss. A loss is backpropagated through the neural network, and each function is derived to find its slope. We can then modify the weights of the neural network in the direction of the correct output. Leading to a function approximation of this function $f_{neuralnetwork}(X_{input}) = O_{expectedoutput}$

@@

Model explainability within the context of neural networks isn't possible today. Model
explainability referrs to firstly considering some input and output from a model. Then
afterwards the model is examined to determine exactly what led to the predicted output.
This concept is simple when we're working with Decision Trees. A decision tree is a tree
whose nodes are representative of an input value and at every node a branch is selected
based on the value of the input value. It is therefore easy to see how to examine the tree
to explain the output. We just follow the branches in the tree. That being said the branches
are created by algorithms like ID3 which construct branches based on the initial dataset used
to construct the tree, but again ID3 follows simple statistics and can be explained properly.

>>>>

The algorithms that are used in traditional state-space searches are for instance Depth-first search (DFS), Breadth-first Search (BFS), Alpha-Beta Pruning Search (AB-Search)\cite{abpruning:dj}, and Monte-Carlo Tree Search (MCTS).

@@

In the algorithm Monte-Carlo Tree Search described by R. Coulom \cite{mcts:coulom}, there is an agent within some environment. Where each node in the environment represents a state-action pair of the environment, by state-action pair what is meant it is some state and the action that brought the agent to that state. This pair should be unique within the environment.

@@

Many algorithms are popular in reinforcement learning, for instance Q-learning\cite{qlearning:watkins}, and many others.

@@

@@

Model explainability within the context of neural networks isn't possible today. Model
explainability referrs to firstly considering some input and output from a model. Then
afterwards the model is examined to determine exactly what led to the predicted output.
This concept is simple when we're working with Decision Trees. A decision tree is a tree
whose nodes are representative of an input value and at every node a branch is selected
based on the value of the input value. It is therefore easy to see how to examine the tree
to explain the output. We just follow the branches in the tree.
